Title

### 2019-02-09 paper/main.tex
Procrastinating by adding random text to paper.

\aclfinalcopy % Uncomment this line for the final submission

@@

\title{Instructions for \confname{} Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

@@

\begin{document}
\maketitle
\begin{abstract}
  Abstract.
\end{abstract}

@@

Natural language inference (NLI) is the task of characterizing entailment and
contradiction relationships between texts.  We seek to improve models which
perform NLI by adding syntactic features into existing models. In particular,
we will primarily investigate the well-known decomposable attention (DA) neural
network \citep{Parikh2016-em} which obtained state of the art results on the
SNLI \citep{Bowman2015-is} dataset at its time of publication while using
drastically fewer parameters than previous NLI models.

We intend to extend the DA model and evaluate new models on SNLI, MultiNLI
\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
\citep{Khot2018-th}.

In general, most NLI tasks are formulated as characterizing the relationship
between a pair of sequences---a premise and a hypothesis. An NLI model should
predict whether the hyothesis is entailed by the premise, contradicts the
premise, or is neutral to the premise.

>>>>

%\aclfinalcopy % Uncomment this line for the final submission

@@

\title{Title}

\author{
  Deric Pang$^\heartsuit$ \quad
  Author 2 \quad
  Author 3 \quad
  Author 4 \\
  $^\heartsuit$Paul G. Allen of Computer Science \& Engineering,
    University of Washington,
    Seattle, WA, USA \\
  $^\diamondsuit$Allen Institute for Artificial Intelligence, Seattle, WA,
    USA \\
  {\tt \{dericp, author2, author3, author4\}@cs.washington.edu} \\
}

@@

\begin{document}
\maketitle
\begin{abstract}
  We show that syntactic information is important when performing natural
  language inference (NLI). We describe new modeling techniques for NLI that
  improve upon previous baselines by adding minimal amounts of syntactic
  information.
\end{abstract}

@@

Natural language inference (NLI) is the task of characterizing entailment and
contradiction relationships between texts.
In general, most NLI tasks are formulated as characterizing the relationship
between a pair of sequences---a premise and a hypothesis. An NLI model should
predict whether the hyothesis is entailed by the premise, contradicts the
premise, or is neutral to the premise.

We seek to improve models which
perform NLI by adding syntactic features into existing models. In particular,
we investigate the well-known decomposable attention (DA) neural network
\citep{Parikh2016-em} which obtained state of the art results on the
SNLI \citep{Bowman2015-is} dataset at its time of publication while using
drastically fewer parameters than previous NLI models.

We extend the DA model and evaluate new models on SNLI, MultiNLI
\citep{Williams2017-uh}, the SNLI and MultiNLI hard splits
\citep{Gururangan2018-lj}, and smaller, domain specific datasets like Scitail
\citep{Khot2018-th}.
